---
title: "NGHS1 Path Model Sensitivity Analyses"
author: "Daniel O'Leary"
date: "April 22, 2019"
output: 
  github_document:
    toc: true
---

# Setup

## Load Packages

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, haven, broom, glmnet, caret, randomForest, lavaan, regsem, semPlot)
```


## Load Data

```{r load data, warning = FALSE}
semTrainingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_sem_training_data.csv")

semTestingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_sem_testing_data.csv")

semAllData <-
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_imputed_new2.csv")
```


# Models

## Stress Psych Pruned Model - minimum waist circumference (cm) - WAISTMIN

```{r}
mod_pysch_stress_pruned_wm <-
  '
    ######################
    ## Latent Variables ##
    ######################


    #################
    ## Regressions ##
    #################  
     
    y10_WAISTMIN ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_WAISTMIN ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y2_STRESS 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y2_STRESS ~ y0_CATINC + y0_RACE + y0_pbmi

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_QI 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y2_STRESS ~~ 0*y0_QI   

    y0_pbmi ~~ 0*y0_CATINC
  
  '

fit_psych_stress_pruned_wm <- 
  sem(
    mod_pysch_stress_pruned_wm, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_pruned_wm, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Psych Pruned Model - minimum waist circumference (cm) - WAISTMIN

```{r}
mod_psych_anx_pruned_wm <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_WAISTMIN ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_WAISTMIN ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y3_ANXR 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y3_ANXR ~ y0_CATINC + y0_pbmi

    y5_AWARE + y5_DISTRST + y5_INEFCT ~ y0_RACE

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_QI 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y3_ANXR ~~ 0*y0_QI + 0*y0_RACE   

    y0_pbmi ~~ 0*y0_CATINC

  '


fit_psych_anx_pruned_wm <-
  sem(
    mod_psych_anx_pruned_wm, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_pruned_wm, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Stress Psych Pruned Model - waist umbilicus circumference (cm) - WAISTUMB

```{r}
mod_pysch_stress_pruned_wu <-
  '
    ######################
    ## Latent Variables ##
    ######################


    #################
    ## Regressions ##
    #################  
     
    y10_WAISTUMB ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_WAISTUMB ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y2_STRESS 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y2_STRESS ~ y0_CATINC + y0_RACE + y0_pbmi

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_QI 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y2_STRESS ~~ 0*y0_QI   

    y0_pbmi ~~ 0*y0_CATINC
  
  '

fit_psych_stress_pruned_wu <- 
  sem(
    mod_pysch_stress_pruned_wu, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_pruned_wu, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Psych Pruned Model - waist umbilicus circumference (cm) - WAISTUMB

```{r}
mod_psych_anx_pruned_wu <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_WAISTUMB ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_WAISTUMB ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y3_ANXR 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y3_ANXR ~ y0_CATINC + y0_pbmi

    y5_AWARE + y5_DISTRST + y5_INEFCT ~ y0_RACE

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_QI 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y3_ANXR ~~ 0*y0_QI + 0*y0_RACE   

    y0_pbmi ~~ 0*y0_CATINC

  '


fit_psych_anx_pruned_wu <-
  sem(
    mod_psych_anx_pruned_wu, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_pruned_wu, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Stress Psych Pruned Model - sum of skin folds (mm) - SUMSKIN

```{r}
mod_pysch_stress_pruned_ss <-
  '
    ######################
    ## Latent Variables ##
    ######################


    #################
    ## Regressions ##
    #################  
     
    y10_SUMSKIN ~ y0_CATINC + y0_SUMSKIN + y0_pbmi + y0_RACE  

    y10_SUMSKIN ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y2_STRESS 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y2_STRESS ~ y0_CATINC + y0_RACE + y0_pbmi

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_SUMSKIN 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_SUMSKIN ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y2_STRESS ~~ 0*y0_SUMSKIN   

    y0_pbmi ~~ 0*y0_CATINC
  
  '

fit_psych_stress_pruned_ss <- 
  sem(
    mod_pysch_stress_pruned_ss, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_pruned_ss, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Psych Pruned Model - sum of skin folds (mm) - SUMSKIN

```{r}
mod_psych_anx_pruned_ss <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_SUMSKIN ~ y0_CATINC + y0_SUMSKIN + y0_pbmi + y0_RACE  

    y10_SUMSKIN ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y3_ANXR 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y3_ANXR ~ y0_CATINC + y0_pbmi

    y5_AWARE + y5_DISTRST + y5_INEFCT ~ y0_RACE

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_SUMSKIN 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_SUMSKIN ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y3_ANXR ~~ 0*y0_SUMSKIN + 0*y0_RACE   

    y0_pbmi ~~ 0*y0_CATINC

  '


fit_psych_anx_pruned_ss <-
  sem(
    mod_psych_anx_pruned_ss, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_pruned_ss, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Stress Psych Pruned Model - arm circumference (cm)

```{r}
mod_pysch_stress_pruned_ac <-
  '
    ######################
    ## Latent Variables ##
    ######################


    #################
    ## Regressions ##
    #################  
     
    y10_ARMCIRAV ~ y0_CATINC + y0_ARMCIRAV + y0_pbmi + y0_RACE  

    y10_ARMCIRAV ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y2_STRESS 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y2_STRESS ~ y0_CATINC + y0_RACE + y0_pbmi

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_ARMCIRAV 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_ARMCIRAV ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y2_STRESS ~~ 0*y0_ARMCIRAV   

    y0_pbmi ~~ 0*y0_CATINC
  
  '

fit_psych_stress_pruned_ac <- 
  sem(
    mod_pysch_stress_pruned_ac, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_pruned_ac, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Psych Pruned Model - arm circumference (cm)

```{r}
mod_psych_anx_pruned_ac <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_ARMCIRAV ~ y0_CATINC + y0_ARMCIRAV + y0_pbmi + y0_RACE  

    y10_ARMCIRAV ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y3_ANXR 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y3_ANXR ~ y0_CATINC + y0_pbmi

    y5_AWARE + y5_DISTRST + y5_INEFCT ~ y0_RACE

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_ARMCIRAV 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_ARMCIRAV ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y3_ANXR ~~ 0*y0_ARMCIRAV + 0*y0_RACE   

    y0_pbmi ~~ 0*y0_CATINC

  '


fit_psych_anx_pruned_ac <-
  sem(
    mod_psych_anx_pruned_ac, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_pruned_ac, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```
