---
title: "NGHS1 Supplemental Analyses"
author: "Daniel O'Leary"
date: "April 15, 2019"
output: 
  github_document:
    toc: true
---

# Setup

## Load Packages
```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, haven, broom, lavaan, mediation, lm.beta)
```


## Load Data

```{r load data, warning = FALSE}
semTrainingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_sem_training_data.csv")

semTestingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_sem_testing_data.csv")

semAllData <-
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_imputed_new2.csv") %>% 
  mutate(y0_pbmi = (y0_WT_fm2 * 703) / (y0_HTFT_fm2 * 12 * y0_HTFT_fm2 * 12))

```


# Models

```{r}
cor.test(semAllData$y2_STRESS, semAllData$y3_ANXR)
```


## Income predicting weight gain

```{r}
income_bmi <-
  lm(
    y10_QI ~
      y0_CATINC + y0_QI,
    data = semAllData
  )

summary(income_bmi)

lm.beta(income_bmi)
```


## Income predicting affect

```{r}
stress_inc <-
  lm(
    scale(y2_STRESS) ~
      scale(y0_CATINC) +
      y0_QI + y0_pbmi + y0_RACE,
    data = semAllData
  )

summary(stress_inc)

lm.beta(stress_inc)

confint(stress_inc)


anx_inc <-
  lm(
    scale(y3_ANXR) ~
      scale(y0_CATINC) +
      y0_QI + y0_pbmi + y0_RACE,
    data = semAllData
  )

summary(anx_inc)

lm.beta(anx_inc)

confint(anx_inc)
```


## Affect predicting weight gain

```{r}
stress_bmi <-
  lm(
    y10_QI ~
      y2_STRESS + y0_QI,
    data = semAllData
  )

summary(stress_bmi)

lm.beta(stress_bmi)


anx_bmi <-
  lm(
    y10_QI ~
      y3_ANXR + y0_QI,
    data = semAllData
  )

summary(anx_bmi)

lm.beta(anx_bmi)

```


## Psychological variables predicting weight gain

```{r}
edi_bmi1 <-
  lm(
    y10_QI ~
      y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT,
    data = semAllData
  )

summary(edi_bmi1)

lm.beta(edi_bmi1)


edi_bmi2 <-
  lm(
    y10_QI ~
      y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT + y0_QI,
    data = semAllData
  )

summary(edi_bmi2)

lm.beta(edi_bmi2)
```


## Eating behavior variables predicting weight gain

```{r}
eat_bmi1 <-
  lm(
    y10_QI ~
      y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y7_SECRET,
    data = semAllData
  )

summary(eat_bmi1)

lm.beta(eat_bmi1)


eat_bmi2 <-
  lm(
    y10_QI ~
      y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y7_SECRET + y0_QI,
    data = semAllData
  )

summary(eat_bmi2)

lm.beta(eat_bmi2)
```


#  Mediation

## Income --> Stress --> Weight

```{r}
lm1 <-
  lm(
    y2_STRESS ~
      y0_CATINC,
    data =
      semAllData %>%
      dplyr::select(y10_QI, y2_STRESS, y0_CATINC) %>%
      distinct() %>%
      filter(!is.na(y10_QI))
  )

summary(lm1)

lm2 <-
  lm(
    y10_QI ~
      y2_STRESS + y0_CATINC,
    data =
      semAllData %>%
      dplyr::select(y10_QI, y2_STRESS, y0_CATINC) %>%
      distinct() %>%
      filter(!is.na(y10_QI))
  )

summary(lm2)


med.output <- mediation::mediate(lm1, lm2, treat = "y0_CATINC", mediator = "y2_STRESS")

summary(med.output)
```


## Income --> Anxiety --> Weight

```{r}
lm1 <-
  lm(
    y3_ANXR ~
      y0_CATINC,
    data =
      semAllData %>%
      dplyr::select(y10_QI, y3_ANXR, y0_CATINC) %>%
      distinct() %>%
      filter(!is.na(y10_QI))
  )

summary(lm1)

lm2 <-
  lm(
    y10_QI ~
      y3_ANXR + y0_CATINC,
    data =
      semAllData %>%
      dplyr::select(y10_QI, y3_ANXR, y0_CATINC) %>%
      distinct() %>%
      filter(!is.na(y10_QI))
  )

summary(lm2)


med.output <- mediation::mediate(lm1, lm2, treat = "y0_CATINC", mediator = "y3_ANXR")

summary(med.output)
```


## Multiple mediation - stress & psychological variables

```{r}
data <-
  data.frame(
    X = semAllData$y0_CATINC,
    X2 = semAllData$y0_QI,
    X3 = semAllData$y0_RACE,
    X4 = semAllData$y0_pbmi,
    Y = semAllData$y10_QI,
    M1 = semAllData$y2_STRESS,
    M2 = semAllData$y5_AWARE,
    M3 = semAllData$y5_INEFCT,
    M4 = semAllData$y5_SELWT,
    M5 = semAllData$y5_DISTRST
  )

model <- 
  '
    # direct effect
      Y ~ b1 * M1 + b2 * M2 + b3 * M3 + b4 * M4 + b5* M5 + c * X + c2 * X2 + c3 * X3 + c4 * X4
    
    # mediator
      M1 ~ a1 * X
      M2 ~ a2 * X
      M3 ~ a3 * X
      M4 ~ a4 * X
      M5 ~ a5 * X  
    
    
    # direct effect
      direct := c
    
    # indirect effect (a*b)
      indirect1 := a1 * b1
      indirect2 := a2 * b2
      indirect3 := a3 * b3
      indirect4 := a4 * b4
      indirect5 := a5 * b5
    
    
    # total effect
      total := c + (a1 * b1) + (a2 * b2)  + (a3 * b3) + (a4 * b4) + (a5 * b5)
      prop_mediated := (abs(indirect1) + abs(indirect2) + abs(indirect3) + abs(indirect4) + abs(indirect5) )/abs(total)
    
    # covariances
    
      M1 ~~ M2 + M3 + M4 + M5
      M2 ~~ M3 + M4 + M5

'
fit <- 
  sem(
    model, 
    data = data
  )

summary(
  fit, 
  standardized = TRUE, 
  fit.measures = T, 
  rsq = T
)
```


## Multiple mediation - anxiety & psychological variables

```{r}
data <-
  data.frame(
    X = semAllData$y0_CATINC,
    X2 = semAllData$y0_QI,
    X3 = semAllData$y0_RACE,
    X4 = semAllData$y0_pbmi,
    Y = semAllData$y10_QI,
    M1 = semAllData$y2_STRESS,
    M2 = semAllData$y5_AWARE,
    M3 = semAllData$y5_INEFCT,
    M4 = semAllData$y5_SELWT,
    M5 = semAllData$y5_DISTRST
  )

model <- 
  '
    # direct effect
      Y ~ b1 * M1 + b2 * M2 + b3 * M3 + b4 * M4 + b5* M5 + c * X + c2 * X2 + c3 * X3 + c4 * X4
    
    # mediator
      M1 ~ a1 * X
      M2 ~ a2 * X
      M3 ~ a3 * X
      M4 ~ a4 * X
      M5 ~ a5 * X  
    
    
    # direct effect
      direct := c
    
    # indirect effect (a*b)
      indirect1 := a1 * b1
      indirect2 := a2 * b2
      indirect3 := a3 * b3
      indirect4 := a4 * b4
      indirect5 := a5 * b5
    
    
    # total effect
      total := c + (a1 * b1) + (a2 * b2)  + (a3 * b3) + (a4 * b4) + (a5 * b5)
      prop_mediated := (abs(indirect1) + abs(indirect2) + abs(indirect3) + abs(indirect4) + abs(indirect5) )/abs(total)
    
    # covariances
    
      M1 ~~ M2 + M3 + M4 + M5
      M2 ~~ M3 + M4 + M5

'
fit <- 
  sem(
    model, 
    data = data
  )

summary(
  fit, 
  standardized = TRUE, 
  fit.measures = T, 
  rsq = T
)
```

