---
title: "NGHS1 Variable Selection"
author: "Daniel O'Leary"
date: "October 29, 2018"
output: github_document
---

# Setup

```{r load pacakges}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, haven, broom, glmnet, caret, randomForest)
```

```{r load data, warning = FALSE}
lassoTrainingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_lasso_training_data.csv") %>% 
  as_data_frame()

set.seed(1987)
```

```{r functions}
# Get best result function
getBestResult = function(caret_fit) {
  best = which(rownames(caret_fit$results) == rownames(caret_fit$bestTune))
  best_result = caret_fit$results[best, ]
  rownames(best_result) = NULL
  best_result
}


plotVarSelection <- function(model, data) {
  num_rows <- nrow(summary(coef(model$finalModel, model$bestTune$lambda)))
  
  coef_sum <- summary(coef(model$finalModel, model$bestTune$lambda))[2:num_rows, "i"]
  
  coefs <- 
    data.frame(
      names(data)[coef_sum - 1], 
      summary(coef(model$finalModel, model$bestTune$lambda))[2:num_rows,3]
    )
  
  names(coefs) <- c("var", "coef")
  
  coefs %>% 
    ggplot(aes(fct_reorder(var, coef), coef)) +
    geom_point() + 
    coord_flip()
}
```

```{r parameters}
# set up parameters
fitControl <-
  trainControl(
    ## 5-fold CV
    method = "repeatedcv",
    number = 5,
    ## repeated ten times
    repeats = 10
  )

fitControl2 <- 
  trainControl(
    ## 5-fold CV
    method = "repeatedcv",
    number = 5,
    ## repeated ten times
    repeats = 10
  )
  
trainGrid <-
  expand.grid(
    alpha = 1,
    lambda = 10^seq(10, -2, length = 100)
  )
```


# Variable selection

## Selection 1: Negative Emotions Predicting Change in BMI

Let's start with the two scales in the dataset that measure emotions, the **Manifest Anxiety Scale** and the **Perceived Stress Scale**. We'll only look at variables up to year 5 because we want to be able to predict the eating disorders inventory at year 5 with these variables.

```{r}
# Select data
psychTrain1 <-
  lassoTrainingData %>% 
  select(
    y10_QI,
    y2_STRESS,
    y4_STRESS,
    y3_ANXR,
    y5_ANXR
  ) %>% 
  filter_all(all_vars(!is.na(.)))

psychTrain1X <- 
  psychTrain1 %>% 
  select(-y10_QI)

psychTrain1Y <-
  psychTrain1 %>% 
  select(y10_QI)
```

```{r, warning = FALSE}
lassoFitPsych1 <- 
  train(
    psychTrain1X, 
    psychTrain1Y$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych1 <-
  train(
    psychTrain1X, 
    psychTrain1Y$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych1, elastic = elnetFitPsych1)
resamples(models) %>% summary()

getBestResult(lassoFitPsych1)
getBestResult(elnetFitPsych1)
```

Elnet selected alpha = 1 which is equivalent to LASSO.

```{r}
coef(elnetFitPsych1$finalModel, elnetFitPsych1$bestTune$lambda)
plotVarSelection(elnetFitPsych1, psychTrain1X)
```

Year 3 anxiety is the only variable selected by the model. We will compare this to year 2 stress for theoretical reasons.

## Selection 2: Income Predicting Negative Emotions

Let's look at which of these emotion variables are predicted by income.

```{r}
# Select data
psychTrain2 <-
  lassoTrainingData %>% 
  select(
    y0_CATINC,
    y2_STRESS,
    y4_STRESS,
    y3_ANXR,
    y5_ANXR
  ) %>% 
  filter_all(all_vars(!is.na(.)))

psychTrain2X <- 
  psychTrain2 %>% 
  select(-y0_CATINC)

psychTrain2Y <-
  psychTrain2 %>% 
  select(y0_CATINC)
```

```{r, warning = FALSE}
lassoFitPsych2 <- 
  train(
    psychTrain2X, 
    psychTrain2Y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych2 <-
  train(
    psychTrain2X, 
    psychTrain2Y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych2, elastic = elnetFitPsych2)
resamples(models) %>% summary()

getBestResult(lassoFitPsych2)
getBestResult(elnetFitPsych2)
```

Elnet selected alpha = 1 which is equivalent to LASSO.

```{r}
coef(lassoFitPsych2$finalModel, lassoFitPsych2$bestTune$lambda)
plotVarSelection(lassoFitPsych2, psychTrain2X)
```

Higher income is associated with lower year 3 anxiety and lower year 2 stress. 

## Selection 3: Eating Surveys Predicting BMI

Next, we'll look at the psychological variables that we're most interested in - ones that are somewhat related to eating. For this step, we have the **Eating Disorders Inventory** and the **Emotional Eating Index**.  If we want to go with one year's worth of variables from the first scale, it seems like it makes sense to go with year 5 as this is the only year after the anxiety score for which we currently have all the data. We'll look at 

```{r}
# Select data
psychTrain3a <-
  lassoTrainingData %>% 
  dplyr::select(
    y10_QI,
    y5_PERFCT,
    y5_AWARE,
    y5_BULIM,
    y5_DISTRST,
    y5_INEFCT,
    y5_FEARS,
    contains("_eat_WORRYMR"),
    contains("_eat_SADMR"),
    contains("_eat_HAPPYMR"),
    contains("_eat_BOREDMR"),
    contains("_eat_REWARD"),
    contains("_eat_MAD"),
    -contains("y0"),
    -contains("y2"),
    -contains("y3")
  )

psychTrain3Xa <- 
  psychTrain3a %>% 
  dplyr::select(-y10_QI)

psychTrain3Ya <-
  psychTrain3a %>% 
  dplyr::select(y10_QI)
```

```{r, warning = FALSE}
lassoFitPsych3a <- 
  train(
    psychTrain3Xa, 
    psychTrain3Ya$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych3a <-
  train(
    psychTrain3Xa, 
    psychTrain3Ya$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych3a, elastic = elnetFitPsych3a)
resamples(models) %>% summary()

getBestResult(lassoFitPsych3a)
getBestResult(elnetFitPsych3a)
```

```{r}
coef(lassoFitPsych3a$finalModel, lassoFitPsych3a$bestTune$lambda)
plotVarSelection(lassoFitPsych3a, psychTrain3Xa)
```


## Selection 4: Income Predicting Eating Surveys

Now let's see which of these variables are associated with income.

```{r}
# Select data
psychTrain5X <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_PERFCT,
    y5_AWARE,
    y5_BULIM,
    y5_DISTRST,
    y5_INEFCT,
    y5_FEARS,
    contains("_eat_WORRYMR"),
    contains("_eat_SADMR"),
    contains("_eat_HAPPYMR"),
    contains("_eat_BOREDMR"),
    contains("_eat_REWARD"),
    contains("_eat_MAD"),
    -contains("y0"),
    -contains("y2"),
    -contains("y3")
  )

psychTrain5Y <-
  lassoTrainingData %>% 
  dplyr::select(y0_CATINC)
```

```{r, warning = FALSE}
lassoFitPsych5 <- 
  train(
    psychTrain5X, 
    psychTrain5Y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych5 <-
  train(
    psychTrain5X, 
    psychTrain5Y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych5, elastic = elnetFitPsych5)
resamples(models) %>% summary()

getBestResult(lassoFitPsych5)
getBestResult(elnetFitPsych5)
```

```{r}
coef(elnetFitPsych5$finalModel, elnetFitPsych5$bestTune$lambda)
plotVarSelection(elnetFitPsych5, psychTrain5X)
```
Higher levels of income are associated with lower levels of AWARE, lower levels of DISTRST.

## Selection 5: Stress Predicting Eating Surveys

Now let's see which of these variables are associated with our stress scale.

```{r}
# Select data
psychTrain4dX <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_PERFCT,
    y5_AWARE,
    y5_BULIM,
    y5_DISTRST,
    y5_INEFCT,
    y5_FEARS,
    contains("_eat_WORRYMR"),
    contains("_eat_SADMR"),
    contains("_eat_HAPPYMR"),
    contains("_eat_BOREDMR"),
    contains("_eat_REWARD"),
    contains("_eat_MAD"),
    -contains("y0"),
    -contains("y2"),
    -contains("y3")
  )

psychTrain4dY <-
  lassoTrainingData %>% 
  dplyr::select(y2_STRESS)
```

```{r, warning = FALSE}
lassoFitPsych4d <- 
  train(
    psychTrain4dX, 
    psychTrain4dY$y2_STRESS, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych4d <-
  train(
    psychTrain4dX, 
    psychTrain4dY$y2_STRESS, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych4d, elastic = elnetFitPsych4d)
resamples(models) %>% summary()

getBestResult(lassoFitPsych4d)
getBestResult(elnetFitPsych4d)
```

```{r}
coef(elnetFitPsych4d$finalModel, elnetFitPsych4d$bestTune$lambda)
plotVarSelection(elnetFitPsych4d, psychTrain4dX)
```

## Selection 6: Anxiety Predicting Eating Surveys

Now let's see which of these variables are associated with our anxiety scale.

```{r}
# Select data
psychTrain4X <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_PERFCT,
    y5_AWARE,
    y5_BULIM,
    y5_DISTRST,
    y5_INEFCT,
    y5_FEARS,
    contains("_eat_WORRYMR"),
    contains("_eat_SADMR"),
    contains("_eat_HAPPYMR"),
    contains("_eat_BOREDMR"),
    contains("_eat_REWARD"),
    contains("_eat_MAD"),
    -contains("y0"),
    -contains("y2"),
    -contains("y3")
  )

psychTrain4Y <-
  lassoTrainingData %>% 
  dplyr::select(y3_ANXR)
```

```{r, warning = FALSE}
lassoFitPsych4 <- 
  train(
    psychTrain4X, 
    psychTrain4Y$y3_ANXR, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych4 <-
  train(
    psychTrain4X, 
    psychTrain4Y$y3_ANXR, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych4, elastic = elnetFitPsych4)
resamples(models) %>% summary()

getBestResult(lassoFitPsych4)
getBestResult(elnetFitPsych4)
```

```{r}
coef(lassoFitPsych4$finalModel, lassoFitPsych4$bestTune$lambda)
plotVarSelection(lassoFitPsych4, psychTrain4X)
```

The variables most consistently selected across 3 - 6 are year 5 interoceptive awareness, year 5 ineffectiveness, and year 5 interpersonal distrust.


## Selection 7: Assorted Psychological Variables Predicting BMI

In this next step, we'll do sort of a grab bag of other psychological variables. What's left in this domain are the **Coping Strategies Inventory** and the **The Perceived Competence Scale for Children**.

```{r}
# Select data
psychTrain7 <-
  lassoTrainingData %>% 
  dplyr::select(
    y10_QI,
    y4_CR1,
    y6_CR1,
    y8_CR1,
    y4_EE1,
    y6_EE1,
    y8_EE1,
    y4_SCRT1,
    y6_SCRT1,
    y8_SCRT1,
    y5_SCHCP, 
    y5_BEHCD, 
    y5_SELWT
  )

psychTrain7X <- 
  psychTrain7 %>% 
  dplyr::select(-y10_QI)

psychTrain7Y <-
  psychTrain7 %>% 
  dplyr::select(y10_QI)
```

```{r, warning = FALSE}
lassoFitPsych7 <- 
  train(
    psychTrain7X, 
    psychTrain7Y$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych7 <-
  train(
    psychTrain7X, 
    psychTrain7Y$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych7, elastic = elnetFitPsych7)
resamples(models) %>% summary()

getBestResult(lassoFitPsych7)
getBestResult(elnetFitPsych7)
```

```{r}
coef(lassoFitPsych7$finalModel, lassoFitPsych7$bestTune$lambda)
plotVarSelection(lassoFitPsych7, psychTrain7X)
```


## Selection 8: Income Predicting Assorted Psychological Variables

```{r}
# Select data
psychTrain6 <-
  lassoTrainingData %>% 
  dplyr::select(
    y0_CATINC,
    y4_CR1,
    y6_CR1,
    y8_CR1,
    y4_EE1,
    y6_EE1,
    y8_EE1,
    y4_SCRT1,
    y6_SCRT1,
    y8_SCRT1,
    y5_SCHCP, 
    y5_BEHCD, 
    y5_SELWT
  )

psychTrain6X <- 
  psychTrain6 %>% 
  dplyr::select(-y0_CATINC)

psychTrain6Y <-
  psychTrain6 %>% 
  dplyr::select(y0_CATINC)
```

```{r warning = FALSE}
lassoFitPsych6 <- 
  train(
    psychTrain6X, 
    psychTrain6Y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych6 <-
  train(
    psychTrain6X, 
    psychTrain6Y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych6, elastic = elnetFitPsych6)
resamples(models) %>% summary()

getBestResult(lassoFitPsych6)
getBestResult(elnetFitPsych6)
```

```{r}
coef(elnetFitPsych6$finalModel, elnetFitPsych6$bestTune$lambda)
plotVarSelection(elnetFitPsych6, psychTrain6X)
```


## Selection 9: Stress Predicting Assorted Psychological Variables

```{r}
# Select data
psychTrain8 <-
  lassoTrainingData %>% 
  dplyr::select(
    y2_STRESS,
    y4_CR1,
    y6_CR1,
    y8_CR1,
    y2_EE1,
    y4_EE1,
    y6_EE1,
    y8_EE1,
    y4_SCRT1,
    y6_SCRT1,
    y8_SCRT1,
    y5_SCHCP,  
    y5_BEHCD, 
    y5_SELWT
  )

psychTrain8X <- 
  psychTrain8 %>% 
  dplyr::select(-y2_STRESS)

psychTrain8Y <-
  psychTrain8 %>% 
  dplyr::select(y2_STRESS)
```

```{r warning = FALSE}
lassoFitPsych8 <- 
  train(
    psychTrain8X, 
    psychTrain8Y$y2_STRESS, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych8 <-
  train(
    psychTrain8X, 
    psychTrain8Y$y2_STRESS, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych8, elastic = elnetFitPsych8)
resamples(models) %>% summary()

getBestResult(lassoFitPsych8)
getBestResult(elnetFitPsych8)
```

```{r}
coef(elnetFitPsych8$finalModel, elnetFitPsych8$bestTune$lambda)
plotVarSelection(elnetFitPsych8, psychTrain8X)
```

## Selection 10: Anxiety Predicting Assorted Psychological Variables

```{r}
# Select data
psychTrain7 <-
  lassoTrainingData %>% 
  dplyr::select(
    y3_ANXR,
    y4_CR1,
    y6_CR1,
    y8_CR1,
    y4_EE1,
    y6_EE1,
    y8_EE1,
    y4_SCRT1,
    y6_SCRT1,
    y8_SCRT1,
    y5_SCHCP, 
    y5_BEHCD, 
    y5_SELWT
  )

psychTrain7X <- 
  psychTrain7 %>% 
  dplyr::select(-y3_ANXR)

psychTrain7Y <-
  psychTrain7 %>% 
  dplyr::select(y3_ANXR)
```

```{r warning = FALSE}
lassoFitPsych7 <- 
  train(
    psychTrain7X, 
    psychTrain7Y$y3_ANXR, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitPsych7 <-
  train(
    psychTrain7X, 
    psychTrain7Y$y3_ANXR, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitPsych7, elastic = elnetFitPsych7)
resamples(models) %>% summary()

getBestResult(lassoFitPsych7)
getBestResult(elnetFitPsych7)
```

```{r}
coef(elnetFitPsych7$finalModel, elnetFitPsych7$bestTune$lambda)
plotVarSelection(elnetFitPsych7, psychTrain7X)
```

The variable most consistently selected across 7-10 was year 5 self-worth. Importantly, this was the only variable that was selected to predict year 10 BMI.


## Selection 11: Health Behavior Predicting BMI

```{r}
# Select data
behavTrain1 <-
  lassoTrainingData %>% 
  dplyr::select(
    y10_QI,
    y5_FSTFOOD4,
    y7_FSTFOOD4,
    y9_FSTFOOD4,
    y5_FSTFOOD5,
    y7_FSTFOOD5,
    y9_FSTFOOD5,
    y4_ALONE,
    y5_ALONE,
    y4_SECRET,
    y5_SECRET,
    y6_SECRET,
    y7_SECRET,
    y9_SECRET,
    y4_EATTV,
    y5_EATTV,
    y6_EATTV,
    y7_EATTV,
    y9_EATTV,
    y0_eat_VITAMINS:y9_eat_BOREDLS,
    -contains("_eat_SECRET"),
    -contains("_eat_ALONE"),
    -contains("DIETLOS"),
    -contains("LOSWT"),
    -contains("WGHLS"),
    -contains("WFAMLY"),
    -contains("EATLESS"),
    -contains("WGHMOR"),
    -contains("BOREDLS"),
    -contains("WGHLES"),
    -contains("BOREDLS"),
    -contains("SADLS"),
    -contains("ASTOLD"),
    -contains("BUYFMLY"),
    -contains("NAG"),
    -contains("PICKEAT"),
    -contains("HAPPYLS"),
    -contains("WORRYLS"),
    -contains("CERTFOOD"),
    -contains("GAINWT"),
    -contains("ALLWNT"),
    -contains("SCHLNCH"),
    -contains("STOPEAT"),
    -contains("BUYFMLY"),
    -contains("SCHLNCH")
    -contains("CERTFOOD"),
    -contains("FRIENDS"),
    -contains("FNSHPLT"),
    -contains("SKIPLNCH"),
    -contains("y9"),
    -contains("y0"),
    -contains("BREAKFST"),
    -contains("PHYSACT"),
    -contains("HOMEWRK"),
    -contains("SPORTEAT"),
    -contains("CRRYLNCH"),
    -contains("FIXOWN"),
    -contains("PARSNACK"),
    -contains("BOREDMR"),
    -contains("EATTV"),
    -contains("VRHUNGY"),
    -contains("DRINK")
  ) %>% 
  dplyr::select(
    -ends_with("MR"),
    -contains("eat_MAD"),
    -contains("REWARD")
  )

behavTrain1x <- 
  behavTrain1 %>% 
  dplyr::select(-y10_QI, -contains("y0"), -contains("y2"), -contains("y3"))

xfactors <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_AFTSNK,
    y7_AFTSNK,
    y9_AFTSNK,
    y4_BREAKFST,
    y5_BREAKFST,
    y6_BREAKFST,
    y7_BREAKFST,
    y8_BREAKFST,
    y9_BREAKFST,
    y5_eat_STOPEAT
  ) %>% 
  mutate_all(as.factor)

behavTrain1x <-
  bind_cols(
    behavTrain1x,
    xfactors
  )

behavTrain1y <-
  behavTrain1 %>% 
  dplyr::select(y10_QI)

behavTrain1 <-
   bind_cols(
    behavTrain1x,
    behavTrain1y
  )

mm <- model.matrix(y10_QI ~ . - 1, behavTrain1)
```

```{r, warning = FALSE}
lassoFitBehav1 <- 
  train(
    mm, 
    behavTrain1y$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitBehav1 <-
  train(
    mm, 
    behavTrain1y$y10_QI, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitBehav1, elastic = elnetFitBehav1)
resamples(models) %>% summary()

getBestResult(lassoFitBehav1)
getBestResult(elnetFitBehav1)
```

```{r}
round(coef(elnetFitBehav1$finalModel, elnetFitBehav1$bestTune$lambda), 2)


tmp_coeffs <- coef(elnetFitBehav1$finalModel, elnetFitBehav1$bestTune$lambda)

coefs <- 
  data.frame(name = tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1], coefficient = tmp_coeffs@x)

coefs %>%
  filter(name != "(Intercept)") %>% 
  ggplot(aes(fct_reorder(name, coefficient), coefficient)) +
  geom_point() +
  coord_flip()
```


## Selection 12: Income Predicting Health Behaviors

```{r}
# Select data
behavTrain2 <-
  lassoTrainingData %>% 
  dplyr::select(
    y0_CATINC,
    y5_FSTFOOD4,
    y7_FSTFOOD4,
    y9_FSTFOOD4,
    y5_FSTFOOD5,
    y7_FSTFOOD5,
    y9_FSTFOOD5,
    y4_ALONE,
    y5_ALONE,
    y4_SECRET,
    y5_SECRET,
    y6_SECRET,
    y7_SECRET,
    y9_SECRET,
    y4_EATTV,
    y5_EATTV,
    y6_EATTV,
    y7_EATTV,
    y9_EATTV,
    y0_eat_VITAMINS:y9_eat_BOREDLS,
    -contains("_eat_SECRET"),
    -contains("_eat_ALONE"),    
    -contains("DIETLOS"),
    -contains("LOSWT"),
    -contains("WGHLS"),
    -contains("WFAMLY"),
    -contains("EATLESS"),
    -contains("WGHMOR"),
    -contains("BOREDLS"),
    -contains("WGHLES"),
    -contains("BOREDLS"),
    -contains("SADLS"),
    -contains("ASTOLD"),
    -contains("BUYFMLY"),
    -contains("NAG"),
    -contains("PICKEAT"),
    -contains("HAPPYLS"),
    -contains("WORRYLS"),
    -contains("CERTFOOD"),
    -contains("GAINWT"),
    -contains("ALLWNT"),
    -contains("SCHLNCH"),
    -contains("STOPEAT"),
    -contains("BUYFMLY"),
    -contains("SCHLNCH")
    -contains("CERTFOOD"),
    -contains("FRIENDS"),
    -contains("FNSHPLT"),
    -contains("SKIPLNCH"),
    -contains("y9"),
    -contains("y0"),
    -contains("BREAKFST"),
    -contains("PHYSACT"),
    -contains("HOMEWRK"),
    -contains("SPORTEAT"),
    -contains("CRRYLNCH"),
    -contains("FIXOWN"),
    -contains("PARSNACK"),
    -contains("BOREDMR"),
    -contains("EATTV"),
    -contains("VRHUNGY"),
    -contains("DRINK"),
    -contains("DRINK")
  ) %>% 
  dplyr::select(
    -ends_with("MR"),
    -contains("eat_MAD"),
    -contains("REWARD")
  )


behavTrain2x <- 
  behavTrain2 %>% 
  dplyr::select(-contains("y0"), -contains("y2"), -contains("y3")) 

behavTrain2y <-
  lassoTrainingData %>% 
  dplyr::select(y0_CATINC)

xfactors <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_AFTSNK,
    y7_AFTSNK,
    y9_AFTSNK,
    y4_BREAKFST,
    y5_BREAKFST,
    y6_BREAKFST,
    y7_BREAKFST,
    y8_BREAKFST,
    y9_BREAKFST,
    y5_eat_STOPEAT
  ) %>% 
  mutate_all(as.factor)

behavTrain2x <-
  bind_cols(
    behavTrain2x,
    xfactors
  )

behavTrain2 <-
   bind_cols(
    behavTrain2x,
    behavTrain2y
  )

mm <- model.matrix(y0_CATINC ~ . - 1, behavTrain2)
```


```{r, warning = FALSE}
lassoFitBehav2 <- 
  train(
    mm, 
    behavTrain2y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitBehav2 <-
  train(
    mm, 
    behavTrain2y$y0_CATINC, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitBehav2, elastic = elnetFitBehav2)
resamples(models) %>% summary()

getBestResult(lassoFitBehav2)
getBestResult(elnetFitBehav2)
```

```{r}
coef(lassoFitBehav2$finalModel, lassoFitBehav2$bestTune$lambda)

tmp_coeffs <- coef(lassoFitBehav2$finalModel, lassoFitBehav2$bestTune$lambda)

coefs <- 
  data.frame(name = tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1], coefficient = tmp_coeffs@x)

coefs %>%
  filter(name != "(Intercept)") %>% 
  ggplot(aes(fct_reorder(name, coefficient), coefficient)) +
  geom_point() +
  coord_flip()
```

## Selection 13: Anxiety Predicting Health Behaviors

```{r}
# Select data
behavTrain4 <-
  lassoTrainingData %>% 
  dplyr::select(
    y3_ANXR,
    y5_FSTFOOD4,
    y7_FSTFOOD4,
    y9_FSTFOOD4,
    y5_FSTFOOD5,
    y7_FSTFOOD5,
    y9_FSTFOOD5,
    y4_ALONE,
    y5_ALONE,
    y4_SECRET,
    y5_SECRET,
    y6_SECRET,
    y7_SECRET,
    y9_SECRET,
    y4_EATTV,
    y5_EATTV,
    y6_EATTV,
    y7_EATTV,
    y9_EATTV,
    y0_eat_VITAMINS:y9_eat_BOREDLS,
    -contains("_eat_SECRET"),
    -contains("_eat_ALONE"),    
    -contains("DIETLOS"),
    -contains("LOSWT"),
    -contains("WGHLS"),
    -contains("WFAMLY"),
    -contains("EATLESS"),
    -contains("WGHMOR"),
    -contains("BOREDLS"),
    -contains("WGHLES"),
    -contains("BOREDLS"),
    -contains("SADLS"),
    -contains("ASTOLD"),
    -contains("BUYFMLY"),
    -contains("NAG"),
    -contains("PICKEAT"),
    -contains("HAPPYLS"),
    -contains("WORRYLS"),
    -contains("CERTFOOD"),
    -contains("GAINWT"),
    -contains("ALLWNT"),
    -contains("SCHLNCH"),
    -contains("STOPEAT"),
    -contains("BUYFMLY"),
    -contains("SCHLNCH")
    -contains("CERTFOOD"),
    -contains("FRIENDS"),
    -contains("FNSHPLT"),
    -contains("SKIPLNCH"),
    -contains("y9"),
    -contains("y0"),
    -contains("BREAKFST"),
    -contains("PHYSACT"),
    -contains("HOMEWRK"),
    -contains("SPORTEAT"),
    -contains("CRRYLNCH"),
    -contains("FIXOWN"),
    -contains("PARSNACK"),
    -contains("BOREDMR"),
    -contains("EATTV"),
    -contains("VRHUNGY"),
    -contains("DRINK")
  ) %>% 
  dplyr::select(
    -ends_with("MR"),
    -contains("eat_MAD"),
    -contains("REWARD")
  )

behavTrain4x <- 
  behavTrain4 %>% 
  dplyr::select(-y3_ANXR, -contains("y0"), -contains("y2"), -contains("y3"))

behavTrain4y <-
  behavTrain4 %>% 
  dplyr::select(y3_ANXR)

xfactors <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_AFTSNK,
    y7_AFTSNK,
    y9_AFTSNK,
    y4_BREAKFST,
    y5_BREAKFST,
    y6_BREAKFST,
    y7_BREAKFST,
    y8_BREAKFST,
    y9_BREAKFST,
    y5_eat_STOPEAT
  ) %>% 
  mutate_all(as.factor)

behavTrain4x <-
  bind_cols(
    behavTrain4x,
    xfactors
  )

behavTrain4 <-
   bind_cols(
    behavTrain4x,
    behavTrain4y
  )

mm <- model.matrix(y3_ANXR ~ . - 1, behavTrain4)
```

```{r, warning = FALSE}
lassoFitBehav4 <- 
  train(
    mm, 
    behavTrain4y$y3_ANXR, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitBehav4 <-
  train(
    mm, 
    behavTrain4y$y3_ANXR, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitBehav4, elastic = elnetFitBehav4)
resamples(models) %>% summary()

getBestResult(lassoFitBehav4)
getBestResult(elnetFitBehav4)
```


```{r}
coef(elnetFitBehav4$finalModel, elnetFitBehav4$bestTune$lambda)

tmp_coeffs <- coef(elnetFitBehav4$finalModel, elnetFitBehav4$bestTune$lambda)

coefs <- 
  data.frame(name = tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1], coefficient = tmp_coeffs@x)

coefs %>%
  filter(name != "(Intercept)") %>% 
  ggplot(aes(fct_reorder(name, coefficient), coefficient)) +
  geom_point() +
  coord_flip()
```


## Selection 14: Stress Predicting Health Behaviors

```{r}
# Select data
behavTrain5 <-
  lassoTrainingData %>% 
  dplyr::select(
    y2_STRESS,
    y5_FSTFOOD4,
    y7_FSTFOOD4,
    y9_FSTFOOD4,
    y5_FSTFOOD5,
    y7_FSTFOOD5,
    y9_FSTFOOD5,
    y4_ALONE,
    y5_ALONE,
    y4_SECRET,
    y5_SECRET,
    y6_SECRET,
    y7_SECRET,
    y9_SECRET,
    y4_EATTV,
    y5_EATTV,
    y6_EATTV,
    y7_EATTV,
    y9_EATTV,
    y0_eat_VITAMINS:y9_eat_BOREDLS,
    -contains("_eat_SECRET"),
    -contains("_eat_ALONE"),    
    -contains("DIETLOS"),
    -contains("LOSWT"),
    -contains("WGHLS"),
    -contains("WFAMLY"),
    -contains("EATLESS"),
    -contains("WGHMOR"),
    -contains("BOREDLS"),
    -contains("WGHLES"),
    -contains("BOREDLS"),
    -contains("SADLS"),
    -contains("ASTOLD"),
    -contains("BUYFMLY"),
    -contains("NAG"),
    -contains("PICKEAT"),
    -contains("HAPPYLS"),
    -contains("WORRYLS"),
    -contains("CERTFOOD"),
    -contains("GAINWT"),
    -contains("ALLWNT"),
    -contains("SCHLNCH"),
    -contains("STOPEAT"),
    -contains("BUYFMLY"),
    -contains("SCHLNCH")
    -contains("CERTFOOD"),
    -contains("FRIENDS"),
    -contains("FNSHPLT"),
    -contains("SKIPLNCH"),
    -contains("y9"),
    -contains("y0"),
    -contains("BREAKFST"),
    -contains("PHYSACT"),
    -contains("HOMEWRK"),
    -contains("SPORTEAT"),
    -contains("CRRYLNCH"),
    -contains("FIXOWN"),
    -contains("PARSNACK"),
    -contains("BOREDMR"),
    -contains("EATTV"),
    -contains("VRHUNGY"),
    -contains("DRINK")
  ) %>% 
  dplyr::select(
    -ends_with("MR"),
    -contains("eat_MAD"),
    -contains("REWARD")
  )

behavTrain5x <- 
  behavTrain5 %>% 
  dplyr::select(-y2_STRESS, -contains("y0"), -contains("y2"), -contains("y3")) 

behavTrain5y <-
  behavTrain5 %>% 
  dplyr::select(y2_STRESS)

xfactors <-
  lassoTrainingData %>% 
  dplyr::select(
    y5_AFTSNK,
    y7_AFTSNK,
    y9_AFTSNK,
    y4_BREAKFST,
    y5_BREAKFST,
    y6_BREAKFST,
    y7_BREAKFST,
    y8_BREAKFST,
    y9_BREAKFST,
    y5_eat_STOPEAT
  ) %>% 
  mutate_all(as.factor)

behavTrain5x <-
  bind_cols(
    behavTrain5x,
    xfactors
  )

behavTrain5 <-
   bind_cols(
    behavTrain5x,
    behavTrain5y
  )

mm <- model.matrix(y2_STRESS ~ . - 1, behavTrain5)
```

```{r, warning = FALSE}
lassoFitBehav5 <- 
  train(
    mm, 
    behavTrain5y$y2_STRESS, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center'), 
    tuneGrid = trainGrid
  )

elnetFitBehav5 <-
  train(
    mm, 
    behavTrain5y$y2_STRESS, 
    method = "glmnet", 
    trControl = fitControl2, 
    preProc = c('scale','center') 
  )

models <- list(lasso = lassoFitBehav5, elastic = elnetFitBehav5)
resamples(models) %>% summary()

getBestResult(lassoFitBehav5)
getBestResult(elnetFitBehav5)
```

```{r}
coef(lassoFitBehav5$finalModel, lassoFitBehav5$bestTune$lambda)

tmp_coeffs <- coef(lassoFitBehav5$finalModel, lassoFitBehav5$bestTune$lambda)

coefs <- 
  data.frame(name = tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1], coefficient = tmp_coeffs@x)

coefs %>%
  filter(name != "(Intercept)") %>% 
  ggplot(aes(fct_reorder(name, coefficient), coefficient)) +
  geom_point() +
  coord_flip()
```

We don't see a ton of overlap between top predictors of BMI and eating behaviors predicted by affect. We select year 5 stop eat, year 6 snackfood, year 4 vitamins, and year 7 secret as these showed up in each of the two categories.
