---
title: "NGHS1 Path Analysis"
author: "Daniel O'Leary"
date: "November 14, 2018"
output: 
  github_document:
    toc: true
---

# Setup

## Load Packages
```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, haven, broom, glmnet, caret, randomForest, lavaan, regsem, semPlot)
```


## Load Data

```{r load data, warning = FALSE}
semTrainingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_sem_training_data.csv")

semTestingData <- 
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_sem_testing_data.csv")

semAllData <-
  read_csv("G:/My Drive/research/projects/phsr1/nghs1/nghs1_data/nghs1_imputed_new2.csv") %>% 
  mutate(y0_pbmi = (y0_WT_fm2 * 703) / (y0_HTFT_fm2 * 12 * y0_HTFT_fm2 * 12))

```


## Check Dimensions

```{r}
dim(semTrainingData)
dim(semTestingData)
```


# Path Models

Good fit for models:

  * Chi-square p-val > 0.05 [not necc. w/ large sample size]
  * TLI >= 0.95
  * CFI >= 0.90
  * RMSEA < 0.08
  * SRMR < 0.08
  
## Stress Psych Initial Model

```{r}
mod_psych_stress_initial <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_QI ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT + y2_STRESS

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y2_STRESS

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT + y2_STRESS ~ y0_CATINC + y0_QI + y0_RACE + y0_pbmi

    y0_QI ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT

    y5_INEFCT ~~ y5_SELWT

    y0_pbmi ~~ y0_CATINC


  '

fit_psych_stress_initial <- 
  sem(
    mod_psych_stress_initial, 
    data = semTrainingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_initial, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Stress Psych Pruned Model

```{r}
mod_psych_stress_pruned <-
  '
    ######################
    ## Latent Variables ##
    ######################


    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_QI ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y2_STRESS 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y2_STRESS ~ y0_CATINC + y0_RACE + y0_pbmi

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_QI 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y2_STRESS ~~ 0*y0_QI   

    y0_pbmi ~~ 0*y0_CATINC
  
  '

fit_psych_stress_pruned <- 
  sem(
    mod_psych_stress_pruned, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_pruned, 
  standardized = TRUE, 
  fit.measures = TRUE,
  rsq = TRUE
)
```


## Stress Psych Pruned Model - Parameter Export

```{r}
standardizedSolution(
  fit_psych_stress_pruned,
  type = "std.all",
  se = TRUE,
  zstat = TRUE,
  pvalue = TRUE,
  ci = TRUE,
  level = 0.95
) %>%
  mutate_if(
    ~any(is.numeric(.)),
    ~round(., 3)
  ) %>%
  write.table(
    "G:/My Drive/research/projects/phsr1/nghs1/nghs1_plots/stress_psych_table_std.csv",
    sep =","
  )
```


## Stress Psych Pruned Model - All Data

```{r}
fit_psych_stress_pruned_ad <-
  sem(
    mod_psych_stress_pruned, 
    data = semAllData, 
    estimator = "MLM"
  )

summary(
  fit_psych_stress_pruned_ad, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


# Anxiety Psych

## Anxiety Psych Initial Model

```{r }
mod_psych_anx_initial <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_QI ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT + y3_ANXR

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y3_ANXR

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT + y3_ANXR ~ y0_CATINC + y0_QI + y0_RACE + y0_pbmi

    y0_QI ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y0_pbmi ~~ y0_CATINC
  '

fit_psych_anx_initial <- 
  sem(
    mod_psych_anx_initial, 
    data = semTrainingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_initial, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Psych Pruned Model

```{r}
mod_psych_anx_pruned <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE  

    y10_QI ~ y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y5_SELWT ~ y3_ANXR 

    y5_AWARE + y5_DISTRST + y5_INEFCT + y3_ANXR ~ y0_CATINC + y0_pbmi

    y5_AWARE + y5_DISTRST + y5_INEFCT ~ y0_RACE

    y5_AWARE + y5_INEFCT + y5_SELWT ~ y0_QI 

    y5_SELWT ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE

    
    #################
    ## Covariances ##
    #################    

    y5_AWARE ~~ y5_DISTRST + y5_INEFCT + y5_SELWT 

    y5_DISTRST ~~ y5_INEFCT + y5_SELWT 

    y5_INEFCT ~~ y5_SELWT 

    y3_ANXR ~~ 0*y0_QI + 0*y0_RACE   

    y0_pbmi ~~ 0*y0_CATINC

  '


fit_psych_anx_pruned <-
  sem(
    mod_psych_anx_pruned, 
    data = semTestingData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_pruned, 
  standardized = TRUE, 
  fit.measures = TRUE,
  rsq = TRUE
)
```


## Anxiety Psych Pruned Model - Parameter Export

```{r}
standardizedSolution(
  fit_psych_anx_pruned, 
  type = "std.all", 
  se = TRUE, 
  zstat = TRUE, 
  pvalue = TRUE, 
  ci = TRUE, 
  level = 0.95
) %>%
  mutate_if(
    ~any(is.numeric(.)), 
    ~round(., 3)
  ) %>%
  write.table(
    "G:/My Drive/research/projects/phsr1/nghs1/nghs1_plots/anx_psych_table_std.csv", 
    sep =","
  )
```


## Anxiety Psych Pruned Model - All Data

```{r}
fit_psych_anx_pruned_ad <-
  sem(
    mod_psych_anx_pruned, 
    data = semAllData, 
    estimator = "MLM"
  )

summary(
  fit_psych_anx_pruned_ad, 
  standardized = TRUE, 
  fit.measures = TRUE, 
  rsq = TRUE
)
```


# Stress Behavior

## Stress Behavior Initial Model

```{r}
mod_behav_stress_initial <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE    

    y10_QI ~ y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET + y2_STRESS

    y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET ~ y2_STRESS

    y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET + y2_STRESS ~ y0_CATINC + y0_QI + y0_RACE + y0_pbmi

    y0_QI ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE


    #################
    ## Covariances ##
    #################  
  
    y6_eat_SNKFOOD2 ~~ y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET 

    y5_eat_STOPEAT ~~ y4_eat_VITAMINS + y7_SECRET 

    y4_eat_VITAMINS ~~ y7_SECRET 

    y0_pbmi ~~ y0_CATINC
    
  '
fit_behav_stress_initial <- 
  sem(
    mod_behav_stress_initial, 
    data = semTestingData %>% mutate(y5_eat_STOPEAT = as.factor(y5_eat_STOPEAT)), 
    estimator = "DWLS", 
    ordered = c("y5_eat_STOPEAT")
  )

summary(
  fit_behav_stress_initial, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Stress Behavior Pruned Model

```{r}
mod_behav_stress_pruned <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE    

    y10_QI ~ y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y7_SECRET 

    y6_eat_SNKFOOD2 ~ y2_STRESS + y0_CATINC + y0_QI + y0_RACE + y0_pbmi
    
    y5_eat_STOPEAT ~ y2_STRESS + y0_QI + y0_RACE
    
    y7_SECRET ~ y2_STRESS 

    y2_STRESS ~ y0_CATINC + y0_pbmi + y0_RACE

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE


    #################
    ## Covariances ##
    #################  
  
    y6_eat_SNKFOOD2 ~~ 0*y5_eat_STOPEAT + y7_SECRET 

    y5_eat_STOPEAT ~~ 0*y7_SECRET 

    y0_pbmi ~~ 0*y0_CATINC
    
  '

fit_behav_stress_pruned <- 
  sem(
    mod_behav_stress_pruned, 
    data = semTestingData %>% mutate(y5_eat_STOPEAT = as.factor(y5_eat_STOPEAT)), 
    estimator = "DWLS", 
    ordered = c("y5_eat_STOPEAT")
  )

summary(
  fit_behav_stress_pruned, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Stress Behavior Pruned Model - Parameter Export

```{r}
standardizedSolution(
  fit_behav_stress_pruned, 
  type = "std.all", 
  se = TRUE, 
  zstat = TRUE, 
  pvalue = TRUE, 
  ci = TRUE, 
  level = 0.95
) %>%
  mutate_if(
    ~any(is.numeric(.)), 
    ~round(., 3)
  ) %>%
  write.table(
    "G:/My Drive/research/projects/phsr1/nghs1/nghs1_plots/stress_behav_table_std.csv", 
    sep =","
  )
```


## Stress Behavior Pruned Model - All Data

```{r}
fit_behav_stress_pruned_ad <-
  sem(
    mod_behav_stress_pruned, 
    data = semAllData %>% mutate(y5_eat_STOPEAT = as.factor(y5_eat_STOPEAT)), 
    estimator = "DWLS", 
    ordered = c("y5_eat_STOPEAT")
  )

summary(
  fit_behav_stress_pruned_ad,
  standardized = TRUE, 
  fit.measures = TRUE
)
```


# Anxiety Behavior

## Anxiety Behavior Initial Model

```{r}
mod_behav_anx_initial <-
  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE    

    y10_QI ~ y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET + y3_ANXR

    y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET ~ y3_ANXR

    y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET + y3_ANXR ~ y0_CATINC + y0_QI + y0_RACE + y0_pbmi

    y0_QI ~ y0_pbmi + y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE


    #################
    ## Covariances ##
    #################  
  
    y6_eat_SNKFOOD2 ~~ y5_eat_STOPEAT + y4_eat_VITAMINS + y7_SECRET 

    y5_eat_STOPEAT ~~ y4_eat_VITAMINS + y7_SECRET 

    y4_eat_VITAMINS ~~ y7_SECRET 

    y0_pbmi ~~ y0_CATINC
    
  '

fit_behav_anx_initial <- 
  sem(
    mod_behav_anx_initial, 
    data = semTrainingData %>% mutate(y5_eat_STOPEAT = as.factor(y5_eat_STOPEAT)), 
    estimator = "DWLS", 
    ordered = c("y5_eat_STOPEAT")
  )

summary(
  fit_behav_anx_initial, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Behavior Pruned Model

```{r}
mod_behav_anx_pruned <-

  '
    #################
    ## Regressions ##
    #################  
     
    y10_QI ~ y0_CATINC + y0_QI + y0_pbmi + y0_RACE    

    y10_QI ~ y6_eat_SNKFOOD2 + y5_eat_STOPEAT + y7_SECRET 

    y6_eat_SNKFOOD2 ~ y0_CATINC + y0_QI + y0_RACE
    
    y5_eat_STOPEAT ~ y3_ANXR + y0_CATINC + y0_QI + y0_pbmi
    
    y7_SECRET ~ y3_ANXR 

    y3_ANXR ~ y0_CATINC + y0_pbmi

    y0_QI ~ y0_pbmi + 0*y0_CATINC + y0_RACE

    y0_pbmi + y0_CATINC ~ y0_RACE


    #################
    ## Covariances ##
    #################  
  
    y6_eat_SNKFOOD2 ~~ 0*y5_eat_STOPEAT + y7_SECRET 

    y5_eat_STOPEAT ~~ 0*y7_SECRET 

    y0_pbmi ~~ 0*y0_CATINC
    
  '

fit_behav_anx_pruned <- 
  sem(
    mod_behav_anx_pruned, 
    data = semTestingData %>% mutate(y5_eat_STOPEAT = as.factor(y5_eat_STOPEAT)), 
    estimator = "DWLS", 
    ordered = c("y5_eat_STOPEAT")
  )

summary(
  fit_behav_anx_pruned, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```


## Anxiety Behavior Pruned Model - Parameter Export

```{r}
standardizedSolution(
  fit_behav_anx_pruned, 
  type = "std.all", 
  se = TRUE, 
  zstat = TRUE, 
  pvalue = TRUE, 
  ci = TRUE, 
  level = 0.95
) %>%
  mutate_if(
    ~any(is.numeric(.)), 
    ~round(., 3)
    ) %>%
  write.table(
    "G:/My Drive/research/projects/phsr1/nghs1/nghs1_plots/anx_behav_table_std.csv", 
    sep = ","
  )
```


## Anxiety Behavior Pruned Model - All Data

```{r}
fit_behav_anx_pruned_ad <-
  sem(
    mod_behav_anx_pruned, 
    data = semAllData%>% mutate(y5_eat_STOPEAT = as.factor(y5_eat_STOPEAT)), 
    estimator = "DWLS", 
    ordered = c("y5_eat_STOPEAT")
  )

summary(
  fit_behav_anx_pruned_ad, 
  standardized = TRUE, 
  fit.measures = TRUE
)
```

